---
title: "rainbowrite"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rainbowrite}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r, echo = FALSE, results = "asis"}
rainbowrite::lol_hooks()
```

## Basic use

For the most basic use, with defaults, just replace `cat`, `message` or `print` with calls to `lolcat`, `lolmessage` or `lolprint`, respectively:

```{r}
x <- runif(30)
print(x)
```

becomes

```{r}
rainbowrite::lolprint(x)
```

containing the same great data, but now with much more unicorn flavour.

## Advanced use

If this is not enough control, you can interact directly with the `rainbowrite::lol` object. This has options that can tune the colour cycling. For example, to cycle colours faster than the default, and with a flatter angle (shifting so that rows cycle faster then columns)

```{r}
lol_faster <- rainbowrite::lol$new(rate = 0.1, angle = pi / 10)
```

This can be passed into `rainbowrite::lolprint` and friends:

```{r}
rainbowrite::lolprint(x, lol = lol_faster)
```

Or can be set as the default

```{r}
lol_faster$set_as_default()
rainbowrite::lolprint(x)
```

## Galaxy brain use

Some packages may not use lolcat, but we may want them to be more colourful.

For example, the `cowsay` package is great:

```{r}
cowsay::say("I wish I was more colourful", "cow")
```

but could do with more colours. Use `rainbowrite::lolify` to create a copy of the target function where some of `cat`, `message` or `print` are replaced by their lol versions

```{r}
lolcow <- rainbowrite::lolify(cowsay::say)
```

and use it as

```{r}
lolcow("These colours mooove me!", "cow", type = "print")
```
